### 2018-07-05 UnintentionalStateConflict/paper3/sections/Formalization.tex
temp

\section{Formalization}~\label{sec:formalization}
This version:
\begin{itemize}
	\item void setters
	\item statements
	\item explicit constructor. (?)
\end{itemize}
\begin{figure*}
	\saveSpaceFig
	\begin{displaymath}
		\begin{array}{l}
			\begin{array}{llrl}
				\text{Program}		& P & \Coloneqq  & \overline{IL} \ e  \\
				\text{Interfaces}   & IL & \Coloneqq & \interfaceMC{I}{I}{MC?}{M} \\
				\text{Constructors} & MC & \Coloneqq & \constructor{I_x}{J.x} \\
				\text{Methods}      & M  & \Coloneqq & \method{I}{m}{I_x}{x}{J}{e}  \mid
													   \absmethod{I}{m}{I_x}{x}{J} \\
				\text{Expressions}  & e  & \Coloneqq & 
				x \mid
				e.m(\overline{e}) \mid
				(I)e \mid 
				\kwnew \; I(\overline{e}) \mid 
				\mylet{I}{x}{e_1}{e_2} \\
				\text{Context}      & \Gamma & \Coloneqq & \overline{x}:\overline{I} \\
				\text{Values}       & v & \Coloneqq & (I)o \\
			\end{array}
		\end{array}
	\end{displaymath}
	\caption{Syntax}\label{fig:syntax}
	\saveSpaceFig
\end{figure*}

@@

>>>>

\section{Formalization}~\label{sec:formalization}
This version:
\begin{itemize}
	\item does not support fluent setters
	\item let-expressions
	\item explicit constructor.
\end{itemize}
\begin{figure*}
	\saveSpaceFig
	\begin{displaymath}
		\begin{array}{l}
			\begin{array}{llrl}
				\text{Program}		& P & \Coloneqq  & \overline{IL} \ e  \\
				\text{Interfaces}   & IL & \Coloneqq & \interfaceMC{I}{I}{MC?}{M} \\
				\text{Constructors} & MC & \Coloneqq & \constructor{I_x}{J.x} \\
				\text{Methods}      & M  & \Coloneqq & \method{I}{m}{I_x}{x}{J}{e}  \mid
													   \absmethod{I}{m}{I_x}{x}{J} \\
				\text{Expressions}  & e  & \Coloneqq & 
				x \mid
				e.m(\overline{e}) \mid
				(I)e \mid 
				\kwnew \; I(\overline{e}) \mid 
				\mylet{I}{x}{e_1}{e_2} \\
				\text{Context}      & \Gamma & \Coloneqq & \overline{x}:\overline{I} \\
				\text{Values}       & v & \Coloneqq & (I)o \\
			\end{array}
		\end{array}
	\end{displaymath}
	\caption{Syntax}\label{fig:syntax}
	\saveSpaceFig
\end{figure*}

@@

\section{Proof}
\subsection{Properties}
\begin{theorem}[Subject Reduction]~\label{theorem_subject}
If $\judgeewf \Gamma {e : I}$ and $e \rightarrow e'$, 
then $\judgeewf \Gamma {e' : I}$.
\end{theorem}
\begin{proof}
See Appendix~\ref{appendix_proof}.
\end{proof}

\begin{theorem}[Progress]~\label{theorem_progress}
Suppose $e$ is a well-typed expression, if $e$ includes 
$\left((J)\emph{\kwnew}\;I()\right).m(\overline{v})$ as a sub-expression, then $\mbody(m, I, J) = (I_0, \overline{I_x} \; \overline{x}, I_e\; e_0)$ and $\num{\overline{x}} = \num{\overline{v}}$ for some $I_0$, $\overline{I_x}$, $\overline{x}$, $I_e$ and $e_0$.
\end{theorem}
\begin{proof}
See Appendix~\ref{appendix_proof}.
\end{proof}

\begin{theorem}[Type Soundness]~\label{theorem_soundness}
If $\judgeewf \o {e : I}$ and $e \to^* e'$ with $e'$ a normal form, then $e'$ is 
a value $v$ with $\judgeewf \o {v:I}$.
\end{theorem}
\begin{proof}
Immediate from Theorem~\ref{theorem_subject} and Theorem~\ref{theorem_progress}.
\end{proof}

\begin{theorem}[Determinacy of One-Step Evaluation]~\label{theorem_determinacy}
	If $t \to t'$ and $t \to t''$, then $t' = t''$.
\end{theorem}
\begin{proof}
See Appendix~\ref{appendix_proof}.
\end{proof}
